---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!-- `devtools::build_readme()` is handy for this. -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE # don't show warnings 
)
```


# lls: Local Least Squares for Information Provision Experiments

<!-- badges: start --> 
[![R-CMD-check](https://github.com/dballaelliott/LLS/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/dballaelliott/LLS/actions/workflows/R-CMD-check.yaml) 
<!-- badges: end -->

This R package implements the Local Least Squares (LLS) estimator for identifying causal effects in information provision experiments. The LLS estimator consistently estimates Average Partial Effects (APE) even when there is strong dependence between belief updating and belief effects.

## Installation 

You can install `lls` from GitHub using:

```r
# install.packages("devtools")
devtools::install_github("dballaelliott/lls")
```

Alternatively, you can install from source by downloading this repository:

```{r, eval = FALSE}
# From the source folder
install.packages("path/to/lls", repos = NULL, type = 'source')

# Or from a built tarball
install.packages("path/to/lls_1.0.0.tar.gz", repos = NULL)
```

## Quick Start

```{r, eval=FALSE}
devtools::install_github("dballaelliott/lls")
# build_vignettes = TRUE gives you some local examples with 
devtools::install_github("dballaelliott/lls", build_vignettes = TRUE)
# now you have vignette('lls-intro')
library(lls)
```

## Quick Start 

```{r quickstart, eval=FALSE}
# Basic usage - Active/Passive Control
result <- iv.lls(
  dat = your_data,
  y = "outcome_variable", 
  x = "posterior",
  r = "learning_rate_variable",
  control.fml = "~ prior + other_controls"
)

# Panel Design
result <- panel.lls(
  dat = your_data,
  dy = "outcome_change",
  dx = "belief_change"
)

# View results and plot
summary(result)
plot(result)
```

## A Simple Example with Simulated Data

The `lls` package comes with a simulated dataset `info.sim` to highlight how the 
syntax works and to make some example plots. 

```{r}
# Load the package
library(lls)
library(data.table)

# Load packaged simulated data
data(info.sim)
setDT(info.sim)  # ensure data.table

info.sim[, alpha_est := (posterior - prior) / (signal - prior)]

# Estimate using IV mode
est <- iv.lls(info.sim, y = "Y", x = "posterior", r = "alpha_est",
    bandwidth = 0.05, control.fml = "prior",
    bootstrap = TRUE, bootstrap.n = 100)

# Print summary
print(est)
```

There is a plot function for `lls` objects. It returns a `ggplot` object, so you can customize it further with standard `ggplot2` functions.

```{r}
library(ggplot2)
plot(est) + 
labs(title = "Heterogeneous Effects of Beliefs by Update Size",
     x = "Change in Beliefs",
     y = "",
     subtitle = "Conditional Average Partial Effect")
```



## Citation

If you use this package, please cite the working paper:

> Balla-Elliott, Dylan (2025). "Identifying Causal Effects in Information Provision Experiments." [arXiv:2309.11387](https://doi.org/10.48550/arXiv.2309.11387)

## License

MIT License - see LICENSE file for details.
