---
title: "Quick Start"
author: "Dylan Balla-Elliott"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7, fig.height = 4.5, 
  cache = FALSE
)
```


This R package implements the estimator proposed in [*Identifying Causal Effects in Information Provision Experiments*](https://pdfs.dballaelliott.com/info_iv.pdf). 

The package handles the multi-step estimation process, including bootstrap inference. It also provides a simple wrapper to visualize the CAPE curve, like in the paper. There are lots of options to customize estimation (and you should experiment with them), but the package also provides sensible defaults to get you started quickly.

# A Simple Example with Simulated Data



The `lls` package comes with a simulated dataset `info.sim` to highlight how the 
syntax works and to make some example plots. 

```{r}
# Load the package
library(lls)
library(data.table)

# Load packaged simulated data
data(info.sim)
setDT(info.sim)  # ensure data.table

info.sim[, alpha_est := (posterior - prior) / (signal - prior)]

# Estimate using IV mode
est <- iv.lls(info.sim, y = "Y", x = "posterior", r = "alpha_est",
    bandwidth = 0.05, control.fml = "prior",
    bootstrap = TRUE, bootstrap.n = 100)

# Print summary
print(est)
```

There is a plot function for `lls` objects. It returns a `ggplot` object, so you can customize it further with standard `ggplot2` functions.

```{r}
plot(est)
```
